### 2014-08-30 fundamentals/intro.tex
adds fundamentals.bib

Cyclus provides a sophisticated and modern, agent-based platform. Previous 
codes were lacking in a number of ways. Cyclus has a number of features that 
overcome those issues.

@@

Modeling the growth of a physics-dependent, international nuclear fuel supply
chain is a difficult problem. To date, it has been treated relatively
lightly. Tools have either focused on macro effects, e.g., the fleet-level
stocks and flows of commodities, or micro effects, e.g., the used fuel
composition fast reactor fuel. Accordingly, each focus has driven the
development of these tools, rendering the task of answering questions between
the macro and micro levels either impossible or difficult and time consuming.

>>>>

In addition to providing the fundamental features expected in fuel cycle 
simulators, the Cyclus paradigm enables two major capabilites that previous 
simulators were lacking. First, it enables simulations at multiple levels of 
fidelity.  It also facilitates direct comparison of modeling methodologies.

@@

Modeling the evolution of a physics-dependent, international nuclear fuel supply
chain is a difficult problem. To date, it has been treated relatively
lightly. Tools have either focused on macro effects, e.g., the fleet-level
stocks and flows of commodities, or micro effects, e.g., the used fuel
composition fast reactor fuel. Accordingly, each focus has driven the
development of these tools, rendering the task of answering questions between
the macro and micro levels either impossible or difficult and time consuming.
